Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-14 main.tex
Updated Benjamin's picture and biography and changed one sentence in mine

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
received his diploma in software engineering in 2018 at the University of Melbourne, Australia. Since 2019, he has been pursuing a Ph.D. at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany. His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed filtering.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
received his diploma in computer science from the Karlsruhe Institute of Technology (KIT), Germany, in 2009. Afterwards, he obtained his Ph.D. in 2013 at the Intelligent Sensor–Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany. Since 2013 he is a senior researcher at the Karlsruhe Institute of Technology (KIT), Germany. His research interests are in the areas of multi-sensor data fusion, distributed and decentralized Kalman filtering, combined stochastic and set-membership approaches to state estimation, and event-based systems.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
received his software engineering diploma in 2018 at the University of Melbourne, Australia. Since 2019, he has been pursuing a Ph.D. at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany. His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed filtering.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
is a professor of Computer Science at the Otto von Guericke University Magdeburg in Germany and head of the Autonomous Multisensor Systems (AMS) group. He received his diploma in computer science from the Karlsruhe Institute of Technology (KIT), Germany, in 2009. Afterward, he obtained his Ph.D. in 2013 at the Intelligent Sensor–Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany. His research interests are in the areas of multi-sensor data fusion, distributed and decentralized Kalman filtering, combined stochastic and set-membership approaches to state estimation, and event-based systems.
\end{IEEEbiography}
